Paper Figures

### 2019-08-29 PaperFigures.Rmd
added boolean cytokine for supp

booleanplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none")+
    theme(text = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=10)+
    labs(x="", y="")
}

@@

```{r cytokine, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
a<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(label="p.format", size=6, label.x=1.3, label.y = (.95*.15))+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4+ T cells")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(label="p.format", size=6, label.x=1.3, label.y = (.95*.02))+
    coord_cartesian(ylim=c(0,.02))

@@

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.x=1.3, label.y=(.98*70))+
    coord_cartesian(ylim=c(0,70))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

b<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))

@@

```{r, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
a<-baseplot(melt, "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(label="p.format", size=6, label.x=1.3, label.y=(.95*.15))+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4+ T cells")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "disease", "value", tb.cols)+ 
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(label="p.format", size=6, label.x=1.3, label.y=(.95*.02))+
    coord_cartesian(ylim=c(0,.02))

@@

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.y=(.98*80))+
    coord_cartesian(ylim=c(0,80))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

b<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.y=(.98*80))+
    coord_cartesian(ylim=c(0,80))

@@

```{r receptor on gata3, fig.width=7.5, fig.height=8}
melt<-melt(phen, id.vars=c("TB","SM", "disease"), measure.vars=c("TH1_GATA3CCR4", "TH1_GATA3CXCR3"))
melt$variable<-gsub("TH1_", "", melt$variable)
melt$variable<-gsub("GATA3", "GATA3+", melt$variable)
melt$variable<-gsub("CXCR3", "CXCR3+", melt$variable)
melt$variable<-gsub("CCR4", "CCR4+", melt$variable)

baseplot(melt, "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.y=(.98*15))+
    coord_cartesian(ylim=c(0,15))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")
```

@@

```{r, proliferation and total cyt, fig.width=15, fig.height=8}
melt<-melt(og, id.vars=c("TB","SM", "disease"), measure.vars=c("OG_freq", "IFNg_freq", "TNFa_freq", "IL4_freq"))

groups <- as_labeller(c("IFNg_freq" = "IFNγ", 
                    "TNFa_freq" = "TNFα", "IL4_freq" = "IL-4", "OG_freq" = "Proliferation"))

allplot(melt, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", labeller = groups, ncol=4)+
    labs(y="(%) Total CD4+ T cells")+
    theme(legend.position="bottom") 
```

```{r, cyt from proliferating, fig.width=12, fig.height=8}
melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg_freq", "TNFa_freq", "IL4_freq"))

groups <- as_labeller(c("IFNg_freq" = "IFNγ", 
                    "TNFa_freq" = "TNFα", "IL4_freq" = "IL-4"))

allplot(melt, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", labeller = groups, ncol=3)+
    labs(y="(%) Proliferating CD4+ T cells")+
    theme(legend.position="bottom") 
```

```{r, marker on proliferating, fig.width=15, fig.height=8}
melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet_freq", "GATA3_freq", "CXCR3_freq", "CCR4_freq"))

melt$variable<-gsub("_freq", "", melt$variable)
melt$variable<-factor(melt$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

allplot(melt, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", ncol=4)+
    labs(y="(%) Total CD4+ T cells")+
    theme(legend.position="bottom") 
```

@@

####There are no differences in Mtb-specific proliferation betweeen SM+ and SM- QF+ individuals. The cytokine production from expanded Mtb-specific CD4+ T cells only differs with regards to IFNγ IL-4 co-production, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still cells that co-produce IFNγ and TNFα. 
```{r og and cyt, fig.width=15, fig.height=8}
a<-baseplot(og, "SM", "OG_freq", ltbi.cols)+
    labs(y="(%) CD4+ T cells")+
    facet_wrap(~TB, labeller = as_labeller(c("LTBI"="Proliferation")))+
    coord_cartesian(ylim=c(0,3))

melt<-melt(ogphen, id.vars=c("TB", "SM"), measure.vars = grep("._._.", names(ogphen)))
test<-melt[-grep("._._._.", melt$variable),]
test<-filter(test, variable!="x_x_x")
test$variable<-factor(test$variable, levels=c(
"T_G_x" ,       
"T_x_x" ,         
"x_G_x" ,         
"T_G_4" ,
"T_x_4" ,         
"x_G_4" ,         
"x_x_4"          
))
test$group<-"TH1/2"
for(i in 1:length(test$group)){
    if(test$variable[i] %in% c("T_G_x", "T_x_x", "x_G_x")){
        test$group[i]<- "TH1"
    }
    else if (test$variable[i] == "x_x_4"){
        test$group[i]<- "TH2"
    }
}

b<-booleanplot(test, "variable", "value", ltbi.cols)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    facet_grid(~group, scales="free_x", space="free_x")+
    labs(y="(%) Proliferating CD4+ T cells")

cowplot::plot_grid(a, b, ncol=2, rel_widths=c(1.25,3.75), align="h")
```

@@

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Proliferating Mtb-Specific cells")

b<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))

@@

```{r luminex, fig.width=12, fig.height=16}
lum<-filter_ltbi(subset(luminex, luminex$Stim=="PEP"))
names(lum)<-gsub("IL", "IL-", names(lum))
names(lum)<-gsub("IFNg", "IFNγ", names(lum))
names(lum)<-gsub("TNFa", "TNFα", names(lum))

@@

booleanplot(melt, "SM", "value", ltbi.cols)+facet_wrap(~variable, scales="free")+
    labs(y="pg/mL")

booleanplot(melt, "SM", "value", ltbi.cols)+facet_wrap(~variable, scales="free")+
    labs(y="pg/mL")+
    coord_cartesian(ylim=c(0,40))
```

@@

#Supplementary
###Peptide-Specific Cytokine Production  
```{r, fig.width=15, fig.height=8}
melt<-melt(subset(CYT, CYT$Stim=="PEP"), 
           id.vars=c("TB","SM"), 
           measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
th_groups <- as_labeller(c("TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))

cyt<-filter_hc(melt)
a<-baseplot(cyt, "SM", "value", healthy.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    labs(y="(%) CD4+ T cells")+coord_cartesian(ylim=c(0,.2))

##Some Boolean Cytokine graphs will go here for posterity
*but I need to make them pretty and I dont' feel like doing that right now*
```{r}
cyt<-filter_ltbi(CYT[CYT$Stim=="PMA",])
test<-melt(cyt, id.vars=c("TB", "SM"), measure.vars = grep("._._._.|._._.._.", names(cyt)))
test$variable<-factor(test$variable, levels=c(
"G_4_13_T", "G_4_x_T", "G_x_13_T", "G_4_13_x", "x_4_13_T","G_4_x_x", "G_x_13_x","x_4_x_T","x_x_13_T",
"G_x_x_T" , "G_x_x_x","x_x_x_T",
"x_4_13_x","x_4_x_x", "x_x_13_x"
))

@@

booleanplot(test, "variable", "value", ltbi.cols)+facet_grid(~th, scales="free", space="free_x")+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="(%) CD4+ T cells",
         title="PMA")
```

@@

booleanplot(test, "variable", "value", ltbi.cols)+facet_wrap(~tf, scales="free_x",ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells",
         title="ICS Assay")

@@

booleanplot(test, "variable", "value", tb.cols)+facet_wrap(~tf, scales="free_x", ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")+
    coord_cartesian(ylim=c(0,55))+
    stat_compare_means(label="p.signif", hide.ns=TRUE, label.y=50, size=10)

@@

```{r og phenotype, fig.width=16, fig.height=8}
ogphen<-filter_ltbi(subset(OGPHEN, OGPHEN$Stim=="PEP"))
#graph phenotype
melt<-melt(ogphen, id.vars=c("TB", "SM"), measure.vars = grep("._._._.", names(ogphen)))
test<-filter(melt, variable!="x_x_x_x")
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

@@

booleanplot(test, "variable", "value", ltbi.cols)+facet_wrap(~tf, scales="free_x", ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="(%) Proliferating Mtb-Specific cells")
```

>>>>

booleanplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none")+
    theme(text = element_text(size=20), axis.text.x = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10)+
    labs(x="", y="")
}

@@

```{r cytokine, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
a<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y = (.95*.15))+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4+ T cells")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y = (.95*.02))+
    coord_cartesian(ylim=c(0,.02))

@@

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=(.98*70))+
    coord_cartesian(ylim=c(0,70))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

b<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))

@@

```{r, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
a<-baseplot(melt, "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=(.95*.15))+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4+ T cells")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "disease", "value", tb.cols)+ 
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=(.95*.02))+
    coord_cartesian(ylim=c(0,.02))

@@

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.y=(.98*80))+
    coord_cartesian(ylim=c(0,80))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

b<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.y=(.98*80))+
    coord_cartesian(ylim=c(0,80))

@@

```{r receptor on gata3, fig.width=7.5, fig.height=8}
phen$TH1_GATA4notCCR4<-rowSums(phen[,grep("TH1_._g_._x", names(phen))])
melt<-melt(phen, id.vars=c("TB","SM", "disease"), measure.vars=c("TH1_GATA3CCR4", "TH1_GATA4notCCR4"))

groups <- as_labeller(c("TH1_GATA3CCR4" = "GATA3+CCR4+", 
                    "TH1_GATA4notCCR4" = "GATA3+CCR4-"))

baseplot(melt, "SM", "value", tb.cols)+    
    facet_wrap(~variable, labeller = groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3)+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")
```

@@

```{r, proliferation and total cyt, fig.width=15, fig.height=8}
groups <- as_labeller(c("OG_freq" = "Proliferation","IFNg_freq" = "IFNγ", 
                    "TNFa_freq" = "TNFα", "IL4_freq" = "IL-4"))

part1<-melt(og, id.vars=c("TB","SM", "disease"), measure.vars="OG_freq")
og<-allplot(part1, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    labs(y="(%) Total CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg_freq", "TNFa_freq"))

one<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, labeller = groups, ncol=2)+
    labs(y="(%) Proliferating CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4_freq"))

two<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, labeller = groups)

cowplot::plot_grid(og, one, two, ncol=3, rel_widths = c(1.2,2,1))
```

```{r, marker on proliferating, fig.width=15, fig.height=8}
melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3"))

tf<-allplot(melt, "TB", "value", all.cols)+    
    labs(y="(%) Proliferating CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("CXCR3", "CCR4"))

cowplot::plot_grid(tf, sm)
```

@@

####There are no differences in Mtb-specific proliferation betweeen SM+ and SM- QF+ individuals. The cytokine production from expanded Mtb-specific CD4+ T cells only differs with regards to IFNγ IL-4 co-production, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still cells that co-produce IFNγ and TNFα. 
```{r og and cyt, fig.width=15, fig.height=8}
groups <- as_labeller(c("OG_freq" = "Proliferation","IFNg_freq" = "IFNγ", 
                    "TNFa_freq" = "TNFα", "IL4_freq" = "IL-4"))

melt<-melt(og, id.vars=c("TB","SM", "disease"), measure.vars="OG_freq")
og<-baseplot(melt, "TB", "value", ltbi.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    coord_cartesian(ylim=c(0,3))+
    labs(y="(%) Total CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg_freq", "TNFa_freq"))
one<-baseplot(melt, "TB", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = groups, ncol=2)+
    labs(y="(%) Proliferating CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4_freq"))
two<-baseplot(melt, "TB", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = groups)

cowplot::plot_grid(og, one, two, ncol=3, rel_widths = c(1.2,2,1))
```

@@

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Proliferating Mtb-Specific cells")

b<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))

@@

```{r luminex, fig.width=12, fig.height=32}
lum<-filter_ltbi(subset(luminex, luminex$Stim=="PEP"))
names(lum)<-gsub("IL", "IL-", names(lum))
names(lum)<-gsub("IFNg", "IFNγ", names(lum))
names(lum)<-gsub("TNFa", "TNFα", names(lum))

@@

a<-baseplot(melt, "SM", "value", ltbi.cols)+facet_wrap(~variable, scales="free")+
    labs(y="pg/mL")

b<-baseplot(melt, "SM", "value", ltbi.cols)+facet_wrap(~variable, scales="free")+
    labs(y="pg/mL")+
    coord_cartesian(ylim=c(0,40))

cowplot::plot_grid(a,b, ncol=1, align = "v")
```

@@

##ICS Supplementary
```{r}
booleanplot2<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=disease))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none")+
    theme(text = element_text(size=20), axis.text.x = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    labs(x="", y="")
}
```

###Boolean PMA
*but I need to make them pretty and I dont' feel like doing that right now*
```{r boolean pma cyt, fig.width=15, fig.height=12}
cyt<-plot_filter(CYT[CYT$Stim=="PMA",])
test<-melt(cyt, id.vars=c("TB", "SM", "disease"), measure.vars = grep("._._._.|._._.._.", names(cyt)))
test<-test[-grep("tbet|gata3|x_x_x_x", test$variable),]
test$variable<-factor(test$variable, levels=c(
"G_4_13_T", "G_4_x_T", "G_x_13_T", "G_4_13_x", "x_4_13_T","G_4_x_x", "G_x_13_x","x_4_x_T","x_x_13_T",
"G_x_x_T" , "G_x_x_x","x_x_x_T",
"x_4_13_x","x_4_x_x", "x_x_13_x"
))

@@

th1.2<-booleanplot2(test[test$th=="TH1/2",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 20)+
    coord_cartesian(ylim=c(0,3))+
    theme(strip.text.y = element_blank(), strip.background.y = element_blank())+
    labs(y="(%) CD4+ T cells")

th1<-booleanplot2(test[test$th=="TH1",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 20)+
    coord_cartesian(ylim=c(0,25))+
    theme(strip.text.y = element_blank(), strip.background.y = element_blank())

th2<-booleanplot2(test[test$th=="TH2",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 20)+
    coord_cartesian(ylim=c(0,3))

cowplot::plot_grid(th1.2, th1, th2, ncol=3, rel_widths = c(8,3.5,3.5))
```

###Boolean Phenotypes
###TH1
```{r pma th1 boolean, fig.width=20, fig.height=18}
phen<-plot_filter(subset(PHEN, PHEN$Stim=="PMA"))

melt<-melt(phen, id.vars=c("TB", "SM", "disease"), measure.vars = grep("TH1_._._._.", names(phen)))
test<-filter(melt, variable!="TH1_x_x_x_x")
test$variable<-gsub("TH1_", "", test$variable)
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

booleanplot2(test, "variable", "value", all.cols)+
    facet_grid(TB~tf, scales="free_x")+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 40)+
    coord_cartesian(ylim=c(0,45))

```
###TH2  
```{r pma th2 boolean, fig.width=20, fig.height=18}
phen<-plot_filter(subset(PHEN, PHEN$Stim=="PMA"))

melt<-melt(phen, id.vars=c("TB", "SM", "disease"), measure.vars = grep("TH2_._._._.", names(phen)))
test<-filter(melt, variable!="TH2_x_x_x_x")
test$variable<-gsub("TH2_", "", test$variable)
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

booleanplot2(test, "variable", "value", all.cols)+
    facet_grid(TB~tf, scales="free_x")+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 40)+
    coord_cartesian(ylim=c(0,45))

###Peptide-Specific Cytokine Production  
```{r, fig.width=15, fig.height=8}
melt<-melt(subset(CYT, CYT$Stim=="PEP"), 
           id.vars=c("TB","SM"), 
           measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
th_groups <- as_labeller(c("TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))

cowplot::plot_grid(b, c, ncol=3)
```

```{r, fig.width=16, fig.height=8}
cyt<-plot_filter(CYT[CYT$Stim=="PEP",])
cyt<-filter(cyt, TB!="HC")
test<-melt(cyt, id.vars=c("TB", "SM", "disease"), measure.vars = grep("._._._.|._._.._.", names(cyt)))
test<-test[-grep("tbet|gata3|x_x_x_x", test$variable),]
test$variable<-factor(test$variable, levels=c(
"G_4_13_T", "G_4_x_T", "G_x_13_T", "G_4_13_x", "x_4_13_T","G_4_x_x", "G_x_13_x","x_4_x_T","x_x_13_T",
"G_x_x_T" , "G_x_x_x","x_x_x_T",
"x_4_13_x","x_4_x_x", "x_x_13_x"
))

booleanplot2(test, "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, exact=FALSE, size=10)+
    coord_cartesian(ylim=c(0,.2))+
    labs(y="(%) CD4+ T cells",
         title="PMA")
```

@@

booleanplot(test, "variable", "value", ltbi.cols)+facet_wrap(~tf, scales="free_x",ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10)+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells",
         title="ICS Assay")

@@

booleanplot(test, "variable", "value", tb.cols)+facet_wrap(~tf, scales="free_x", ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")+
    coord_cartesian(ylim=c(0,55))+
    stat_compare_means(method="wilcox.test",label="p.signif", hide.ns=TRUE, label.y=50, size=10)

@@

##Proliferation Supplementary
```{r}
ogphen<-filter_ltbi(subset(OGPHEN, OGPHEN$Stim=="PEP"))
melt<-melt(ogphen, id.vars=c("TB", "SM"), measure.vars = grep("._._.", names(ogphen)))
test<-melt[-grep("._._._.", melt$variable),]
test<-filter(test, variable!="x_x_x")
test$variable<-factor(test$variable, levels=c(
"T_G_x" ,       
"T_x_x" ,         
"x_G_x" ,         
"T_G_4" ,
"T_x_4" ,         
"x_G_4" ,         
"x_x_4"          
))
test$group<-"TH1/2"
for(i in 1:length(test$group)){
    if(test$variable[i] %in% c("T_G_x", "T_x_x", "x_G_x")){
        test$group[i]<- "TH1"
    }
    else if (test$variable[i] == "x_x_4"){
        test$group[i]<- "TH2"
    }
}

booleanplot(test, "variable", "value", ltbi.cols)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    facet_grid(~group, scales="free_x", space="free_x")+
    labs(y="(%) Proliferating CD4+ T cells")

```{r og phenotype, fig.width=16, fig.height=8}
#graph phenotype
melt<-melt(ogphen, id.vars=c("TB", "SM"), measure.vars = grep("._._._.", names(ogphen)))
test<-filter(melt, variable!="x_x_x_x")
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

@@

booleanplot(test, "variable", "value", ltbi.cols)+facet_wrap(~tf, scales="free_x", ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="(%) Proliferating Mtb-Specific cells")
```
